Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-21 paper.qmd
Updated with another projection but need to cheack in the second one why the circle's aspect ratio is different

# Apply the scaling function to the s_curve_noise data
scaled_s_curve_true <- scale_data_manual(
  true_model_df |> select(-ID)) |>
  as_tibble()

# projection <- cbind(
#     c(0.24288,-0.03628,-0.03302,0.12182,-0.04150,0.02344,0.05910),
#     c(0.05019,0.07165,-0.20131,-0.16200,-0.05343,0.06854,-0.00551))

projection <- cbind(
  c(0.5898,-0.4620,-0.1362,0.2047,-0.3680,0.1032,-0.4818),
  c(0.1756,0.0257,0.3683,0.2400,-0.5518,-0.4573,0.5115))

@@

projection <- cbind(
    c(0.03685,-0.02239,0.08047,0.22415,-0.10295,0.04529,0.10381),
    c(-0.16908,0.11691,0.04886,0.10189,-0.00203,-0.09763,-0.13207))

@@

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

# axis_scale <- 2 * limits/3
# axis_pos <- -0.4 * limits

axis_scale <- limits/6
axis_pos <- -2/3 * limits

@@

# axis_scale <- 0.1 * limits
# axis_pos <- -0.4 * limits
# adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

>>>>

# Scaling the true model and add the mean of scaled noise dimensions
scaled_s_curve_true <- scale_data_manual(
  true_model_df |> 
    select(-ID) |>
    select(x1:x3)) |>
  as_tibble() |>
  mutate(x4 = mean(scaled_s_curve_noise$x4),
         x5 = mean(scaled_s_curve_noise$x5),
         x6 = mean(scaled_s_curve_noise$x6),
         x7 = mean(scaled_s_curve_noise$x7))

projection <- cbind(
    c(-0.2782,0.2156,0.1410,0.8068,0.0804,-0.0315,0.4449),
    c(-0.6090,0.3014,-0.1654,-0.3381,-0.0964,0.5900,0.1979))

@@

projection <- cbind(
    c(-0.6296,-0.1452,0.3314,0.2259,-0.4488,-0.0053,-0.4693),
    c(0.5314,0.4634,0.1431,0.2129,-0.0107,0.1477,-0.6443))

@@

@@
